Further Evidence of Modified Spin-down in Sun-like Stars:\\Pile-ups in the Temperature--Period Distribution

### 2022-03-31 src/ms.tex
adding references

Recently, \citet{LorenzoOliveira2019} studied the \prot--age relation of solar twins observed by the Kepler mission, finding marginal statistical evidence in favor of a standard spin-down model over the WMB model. Those authors posited that if WMB takes place for Sun-like stars, it should happen at \rocrit~$\gtrsim 2.29$ or ages~$\gtrsim$~5.3~Gyr.\footnote{A case study of an $\sim$8~Gyr solar twin further reinforced these conclusions \citep{LorenzoOliveira2020}.} By comparison, our findings provide support for the WMB model among stars that are slightly hotter than the Sun, but at \rocrit~$\lesssim$~2 and at ages in the range of $\sim$2--6~Gyr. In contrast to the findings of those authors, we find that the long-period pile-up lies clearly below an empirical 2.5~Gyr gyrochrone of \citet{Curtis2020} that is evolved forward to 5.3~Gyr for braking indices of $n=0.5$ or $n=0.65$.

>>>>

Recently, \citet{LorenzoOliveira2019} studied the \prot--age relation of solar twins observed by the Kepler mission, finding marginal statistical evidence in favor of a standard spin-down model over the WMB model. Those authors posited that if WMB takes place for Sun-like stars, it should happen at \rocrit~$\gtrsim 2.29$ or ages~$\gtrsim$~5.3~Gyr. A case study of an $\sim$8~Gyr solar twin further reinforced these conclusions \citep{LorenzoOliveira2020}. \edit1{Additionally, \citet{doNascimento2020} studied the rotation period distribution of 193 solar analogs, concluding that some solar-mass main-sequence stars appear to rotate significantly more slowly than the Sun, seemingly at odds with the WMB model.} By comparison, our findings provide support for the WMB model among stars that are slightly hotter than the Sun, but at \rocrit~$\lesssim$~2 and at ages in the range of $\sim$2--6~Gyr. In contrast to the findings of those authors, we find that the long-period pile-up lies clearly below an empirical 2.5~Gyr gyrochrone of \citet{Curtis2020} that is evolved forward to 5.3~Gyr for braking indices of $n=0.5$ or $n=0.65$.
